---
title: "Lab 00 - Hello IDS!"
author: "Jamie Ewen"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Jamie", "Adam", "Ben", "Gigi", "Dylan","Yara"),
  
  github_username = c("jamieewen", "Adcel27", "ben-251", "Gand0m", "dylanhoblman","yarakanaann"),
  
  colour = c("red", "green", "plum", "hotpink", "blue", "peachpuff"),
  
  hobby = c("football", "Skiing", "badminton", "volleyball", "football","basketball"),
  
  favourite_number = c(9, 3, 6, 4, 6, 7),
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar Graph of favourite numbers

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "Favourite numbers")
```

It labels each axis and title

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

By changing the colours of the bars so you can tell what you're looking at 
